Shiny App Manuscript Figures: Aquatic Organisms

### 2022-01-11 App_Nonessential/TeamX_Manuscript_Figures/Manuscript_Figures_TeamX.Rmd
reformat figure 7 x axis

Group_size <- aoc_setup %>% 
  ggplot(aes(x = size.length.um.used.for.conversions, fill = org_f)) +
  geom_histogram(bins = 20, color = "black") +
  scale_fill_manual(values = c('#a50026','#d73027','#f46d43','#fdae61','#fee090','#ffffbf','#e0f3f8','#abd9e9','#74add1','#4575b4','#313695', '#641e16')) +
  ylab("Number of Observations")+
  xlab("Particle Length (µm)") +
  theme_classic() +
  theme(text = element_text(size = 12)) +
  scale_x_log10()+
  labs(fill = "Organism Group")

@@

Endpoint_size <- aoc_setup %>% 
  ggplot(aes(x = size.length.um.used.for.conversions, fill = lvl1_f)) +
  geom_histogram(bins = 20, color = "black") +
  scale_fill_manual(values = c('#d73027','#f46d43','#fdae61','#fee090','#ffffbf','#e0f3f8','#abd9e9','#74add1','#4575b4')) +
  xlab("Particle Length (µm)") +
  ylab("Number of Observations")+
  theme_classic() +
  theme(text = element_text(size = 12)) +
  scale_x_log10()+
  labs(fill = "Endpoint Category")

>>>>

Group_size <- aoc_setup %>% 
  ggplot(aes(x = size.length.um.used.for.conversions, fill = org_f)) +
  geom_histogram(bins = 20, color = "black") +
  scale_fill_manual(values = c('#a50026','#d73027','#f46d43','#fdae61','#fee090','#ffffbf','#e0f3f8','#abd9e9','#74add1','#4575b4','#313695', '#641e16')) +
  ylab("Number of Observations")+
  xlab("Particle Length (µm)") +
  theme_classic() +
  theme(text = element_text(size = 12),
        axis.text.x = element_text(margin = margin(t = 10))) +
  scale_x_log10(labels = scales::label_number(accuracy = 1))+
  annotation_logticks(sides = "b", outside = TRUE)+
  coord_cartesian(clip = "off")+
  scale_y_continuous(expand = c(0,0))+
  labs(fill = "Organism Group")

@@

Endpoint_size <- aoc_setup %>% 
  ggplot(aes(x = size.length.um.used.for.conversions, fill = lvl1_f)) +
  geom_histogram(bins = 20, color = "black") +
  scale_fill_manual(values = c('#d73027','#f46d43','#fdae61','#fee090','#ffffbf','#e0f3f8','#abd9e9','#74add1','#4575b4')) +
  xlab("Particle Length (µm)") +
  ylab("Number of Observations")+
  theme_classic() +
  theme(text = element_text(size = 12),
        axis.text.x = element_text(margin = margin(t = 10))) +
  scale_x_log10(labels = scales::label_number(accuracy = 1))+
  annotation_logticks(sides = "b", outside = TRUE)+
  coord_cartesian(clip = "off")+
  scale_y_continuous(expand = c(0,0))+
  labs(fill = "Endpoint Category")
